### 2016-10-28 capability-machine.tex
comments inserted about examples

%Comments
\newcommand\lau[1]{{\color{purple} \sf \footnotesize {LS: #1}}\\}
\newcommand\dominique[1]{{\color{purple} \sf \footnotesize {DD: #1}}\\}
\newcommand\kars[1]{{\color{purple} \sf \footnotesize {LB: #1}}\\}

@@

\section{Examples}
\label{sec:examples}
\subsection{Simple Examples Using Local Capabilities}
\label{subsec:example-loc-cap}
\subsubsection{Simple use of local capabilities}
\begin{verbatim}
let f = fun adv =>
          let l = 1 in
          adv(l);
          l := 1;
          adv(0);
          return *l
\end{verbatim}
In this example \texttt{let l = 1 in} allocates a new local capability \texttt{l} with read-write permissions. Assuming \texttt{adv} has no access to capabilities with permit write local, they cannot store \texttt{l} and thus change its value in the second call.

\subsection{Simple well-bracketness/local capability example}
\begin{verbatim}
let f = fun adv =>
          let x = 1 in
          adv();
          assert(x == 1);
          x := 2;
          adv();
          return 0
\end{verbatim}
A sensible calling scheme uses local capabilities for the continuation capability passed to the callee. In the above example, if \texttt{adv} can store the continuation, then 
\texttt{adv} can invoke it during the second call and thus force the assertion to fail.

>>>>

%Comments
\newcommand\lau[1]{{\color{purple} \sf \footnotesize {LS: #1}}\\}
\newcommand\dominique[1]{{\color{purple} \sf \footnotesize {DD: #1}}\\}
\newcommand\lars[1]{{\color{purple} \sf \footnotesize {LB: #1}}\\}

@@

\section{Examples}
\label{sec:examples}
\subsection{Simple Examples Using Local Capabilities}
\label{subsec:example-loc-cap}
\subsubsection{Simple use of local capabilities}
\begin{verbatim}
let f = fun adv =>
          let l = 1 in
          adv(l);
          l := 1;
          adv(0);
          return *l
\end{verbatim}
In this example \texttt{let l = 1 in} allocates a new local capability \texttt{l} with read-write permissions. Assuming \texttt{adv} has no access to capabilities with permit write local, they cannot store \texttt{l} and thus change its value in the second call.
\lars{So this means that the value returned by *l is 1, correct ? We
  could add an assert statement to the example to show it more directly.}

\lars{What about an even simpler example, such as the one below:}
\begin{verbatim}
let f = fun adv =>
          let l = 1 in
          adv();
          assert (l == 1)
\end{verbatim}

\subsection{Simple well-bracketness/local capability example}
\begin{verbatim}
let f = fun adv =>
          let x = 1 in
          adv();
          assert(x == 1);
          x := 2;
          adv();
          return 0
\end{verbatim}
A sensible calling scheme uses local capabilities for the continuation capability passed to the callee. In the above example, if \texttt{adv} can store the continuation, then 
\texttt{adv} can invoke it during the second call and thus force the assertion to fail.
\lars{don't you want to allocate the location \texttt{x} first and then
  return a function taking \texttt{adv} as an argument ??}
